### 2016-02-01 AssignmentXI/Assignment10-Ditz_Schroeder-WS15-16.tex
number 1

\section{Theoretical Assignment - \textit{Coverage statistics}}
\subsection{}
\subsection{}
\subsection{}
\section{Theoretical Assignment - \textit{Application of the arrival statistic for unitigs}}

>>>>

\section{Theoretical Assignment - \textit{Coverage statistics}}
\subsection{fraction sequenced}
The used equation is from the script(equation \ref{fraction}.\\	
	\begin{eqnarray}
		f=1-e^{-c} \label{fraction}\\
	\end{eqnarray}
\\	
As a result of using the given coverages $c=1,2,4,8, 14$, table \ref{fractionsTable} is deduced. The last column shows the bases which are not covered when the sequence length is  $L= 248956422 bp$ like in the human chromosome 1.
\\
\begin{tabular}{|c|c|c|c|}
	\hline coverage & fraction covered f & fraction not covered & bases not covered [bp] \\ 
	\hline 1 & 0.63212 & 0.36788 & 91586089 \\ 
	\hline 2 & 0.86466 & 0.13534 & 33693762 \\ 
	\hline 4 & 0.98168 & 0.01832 & 4650882 \\ 
	\hline 8 & 0.99966 & 0.00034 & 84645 \\ 
	\hline 14 & 0.99995 & 0.00005 & 12448 \\ 
	\hline 
	\label{fractionsTable}
\end{tabular} 
\\
The Treponema pallidum chromosome has a length of 1,139,633 bp. If now less than one base can be missed, the not covered fraction is $\leq\frac{1}{1,139,633} =7.16*10^{-6}$. This results in a positive fraction of at least 0.999993.  The coverage is determined with the transformed equation \ref{transformedEquation1} and has a value of 11.87.
\\
\begin{equation}
c=-ln(1-f)
\label{transformedEquation1}
\end{equation}
\\
\subsection{times sequenced}
If there is a coverage of $c=10$, a base has been exactly been sequenced three times with a probability p(3)=0.015 according to the poisson distribution (equation \ref{pois}).
\\
\begin{equation}
p(x)=\frac{c^x}{x!} e^{-c} \label{pois}
\end{equation}
\begin{equation}
p(x)=\frac{10^3}{3!} e^{-10} = 0.015
\end{equation}
The next question was at most three times covered. This can be calculated with equation \ref{poisD}. F(3) has a value of $F(3)=0.018$.

\begin{equation}
	F(n)= \sum_{x=0}^{3} p(x) \label{poisD}	
\end{equation}
\begin{equation}
	F(3)= \frac{10^0}{0!}*e^{-10}+\frac{10^1}{1!}*e^{-10}+\frac{10^2}{2!}*e^{-10}+\frac{10^3}{3!}*e^{-10} = 0.018 \label{poisD}	
\end{equation}
\\
\subsection{}
expected number of gaps
mean contig size
\\
\section{Theoretical Assignment - \textit{Application of the arrival statistic for unitigs}}
